\vspace{-2cm} Government websites as data: A methodological pipeline with application to the websites of municipalities in the United States

### 2018-06-14 paper/manuscript.tex
stm results
revising abstract and second section

%============Article Title, Authors==================
\title{\vspace{-2cm} Government websites as data: A methodological pipeline for collection, processing, and text analysis }

@@

A local government's website is a standard and general source of information for citizens and other community stakeholders. Accordingly, government websites have become prominent sources of data for a variety of research agendas in public administration, public policy, and political science. Existing research has relied on manual methods of website data collection and processing. However, reliance on manual collection and processing limits the scale and scope of website content analysis.  We develop a methodological pipeline that researchers can follow in order to gather, process, and analyze website content with established text analysis techniques. First, for the acquisition of website data, we cover approaches to automated scraping methods. Second, pre-processing is a particularly vital step in text analysis, but when websites are concerned, additional measures need to be taken in order to guard against potential sources of bias. We propose a new method for dealing with the kind of duplicated content that is commonly found in government websites. Finally, we illustrate methods of text analysis using automatically gathered and pre-processed website content. We illustrate our methodological pipeline through a new and innovative dataset---the websites of municipal governments in Indiana and Louisiana. We build upon recent research that analyzes how change and variation in the partisan control of government relates to content made available on the government's website. We explore the association between mayoral partisanship and the content of city websites.
%\noindent We explore the effect of transitions of power in municipal governments on the content of their websites. We hypothesize that when party control changes, city administrators modify the contents of their websites in order to fit the agenda of the new incumbent. To test this theory, we study cities in Indiana and Louisiana, two states in which all municipal elections are partisan and the parties of the candidates appear on the ballots. Snapshots of websites before and after transitions of power are acquired through the Wayback Machine. We apply statistical topic models based in latent dirichlet allocation, focusing on changes to the websites. We present results on both which topics see the greatest degree of change associated with transitions in city administrations, and how the topics modified differ with regard to political parties.

@@

\section{The Significance of Government Website Content}
% \cite{grimmelikhuijsen2012developing} conduct an enormously relevant study. Insofar as we analyze what predicts openness of government websites, we will be replicating and building upon this study. They focus on Dutch municipal websites, and their approach is fairly limited in scope and highly manual (which we can compliment). For example, one of the dependent variables ``Decision-making transparency,'' is measured ``using a discrete (1/0) indicator for whether the underlying principles or reasons for local air pollution policies were given on the Web site.''

 According to \cite{Mayhew1974}, politicians engage in advertising, credit claiming and position taking in order to get re-elected. Official city websites allow mayors to do all three. Their offices frequently take a prominent position on the frontpage, and many websites also feature a picture of the candidate. In local politics, where campaign funds are low, this lends the incumbent a crucial advantage in becoming more well-known among her constituents. Furthermore, municipal politics gives incumbents clear and tangible achievements they can point to, such as completed infrastructure projects, the acquisition of federal or state funding, or the hosting of city-wide events. City websites present an opportunity for local officials to brandish these accomplishments. Finally, they also give mayors a platform from which they can advertise their political beliefs. On municipal websites, this may not manifest in the form of brazen partisanship, but more subtle avenues are available. As noted by \cite{einstein2016mayors}, there are stark differences in the spending preferences of Democratic and Republican mayors. City websites can then be used to communicate the stance of a mayor on social or economic programs. Another advantage of websites with regard to communication is that unlike direct social interactions, officials have full control over them.

Some papers on how government websites are used
\begin{itemize}
\item \cite{sandoval2012government}, p.S74, ``Usually citizens access government websites to find information and
data for decision making''.
\item In a survey conducted among a random sample of citizens in the state of Georgia in 2000, \cite{thomas2003new} found that nearly 25\% of internet users in the sample reported visiting a local government website in the previous twelve months to gather information. We would expect that number to be even larger nearly two decades later.
\item \cite{tolbert2006effects} p. 355, ``We ?nd that users of local government Web sites are more likely to trust local governments, controlling for other demo-graphic factors, and that the use of government Web sites is associated with other positive attitudes, espe-cially for federal and local governments. ''
\end{itemize}

In addition to the use of city websites for the politicians that control them, variance in content also matters  with regard to the people who visit them. Local residents likely rely on city websites to get news about events, hot-button political issues specific to their city, contact city officials or find out addresses or opening hours of city institutions. Visitors use city websites to look up local attractions, which are often described in great detail. Similarly, prospective residents looking to move, might rely on city websites to inform their decision on whether to relocate there. An inviting website emphasizing the city's receptiveness to new residents might make a real difference here. Finally, city websites frequently feature sections on business, but there is a lot of variance in this area: Some emphasize economic development, properties, or transportation, whereas others focus on undeveloped land and other business opportunities. Differences in websites likely say something about a city's economic profile, with potential repercussions for the political realm.

@@

>>>>

%============Article Title, Authors==================
\title{\vspace{-2cm} Government websites as data: A methodological pipeline with application to the websites of municipalities in the United States}

@@

A local government's website is arguably the most important general source of information about city policies and processes for residents and other community stakeholders. Accordingly, government websites have become prominent sources of data for a variety of research agendas in public administration, public policy, and political science. Existing research has relied on manual methods of website data collection and processing. However, reliance on manual collection and processing limits the scale and scope of website content analysis. Relying on manual data collection requires that researchers focus on a limited number of websites and/or limited types of site content.  We develop a methodological pipeline that researchers can follow in order to gather, process, and analyze website content with established text analysis techniques. First, for the acquisition of website data, we cover approaches to automated scraping methods. Second, pre-processing is a particularly vital step in text analysis, but when websites are concerned, additional measures need to be taken in order to guard against potential sources of bias. We propose a new method for dealing with the types of duplicated and boilerplate contents that are commonly found in government websites. We illustrate our methodological pipeline through the collection and analysis of a new and innovative dataset---the websites of over two hundred municipal governments in the United States. We build upon recent research that analyzes how variation in the partisan control of government relates to content made available on the government's website. Using a structural topic model to analyze municipal website contents, we find that websites of cities with Democratic mayors include more information about policy deliberation and crime control, whereas websites from cities with Republican mayors include more information about .
%\noindent We explore the effect of transitions of power in municipal governments on the content of their websites. We hypothesize that when party control changes, city administrators modify the contents of their websites in order to fit the agenda of the new incumbent. To test this theory, we study cities in Indiana and Louisiana, two states in which all municipal elections are partisan and the parties of the candidates appear on the ballots. Snapshots of websites before and after transitions of power are acquired through the Wayback Machine. We apply statistical topic models based in latent dirichlet allocation, focusing on changes to the websites. We present results on both which topics see the greatest degree of change associated with transitions in city administrations, and how the topics modified differ with regard to political parties.

@@

\section{The Significance of Government Website Content}

 According to \cite{Mayhew1974}, politicians engage in advertising, credit claiming and position taking in order to get re-elected. Official city websites allow mayors to perform all three of these functions. Their offices frequently take a prominent position on the front page, and many websites also feature a picture of the mayor. We present an example of this in Figure \ref{fig:eriemayor}. The Erie, Pennsylvania website homepage presents an image of Democratic mayor, Joseph Schember, along with a list of laudable attributes of the city. In local politics, where campaign funds are low, this lends the incumbent a crucial advantage in becoming more well-known among her constituents. Furthermore, municipal politics gives incumbents clear and tangible achievements they can point to, such as completed infrastructure projects, the acquisition of federal or state funding, or the hosting of city-wide events. City websites present an opportunity for local officials to brandish these accomplishments. Finally, they also give mayors a platform from which they can advertise their political beliefs. On municipal websites, this may not manifest in the form of brazen partisanship, but more subtle avenues are available. As noted by \cite{einstein2016mayors}, there are stark differences in the spending preferences of Democratic and Republican mayors. City websites can then be used to communicate the stance of a mayor on social or economic programs. Another advantage of websites with regard to communication is that unlike direct social interactions, officials have full control over them.

\begin{figure}
\centering
\includegraphics[scale=0.35]{figures/eriemayor}
\caption{Screenshot from the homepage at \url{http://www.erie.pa.us/}, accessed on 06/14/2018. Image depicts  Democratic mayor of Erie, PA, Joseph Schember.}
\label{fig:eriemayor}
\end{figure}

Members of the public visit municipal government websites for a wide variety of purposes \citet{sandoval2012government}, and with significant regularity. In a survey conducted among a random sample of citizens in the state of Georgia in 2000---nearly two decades ago---found that 25\% of internet users reported visiting a local government website in the previous twelve months \citep{thomas2003new}. Furthermore, the use of a local government website is associated with an individual's perspective on government. \citet{tolbert2006effects} finds that users of local government Web sites are more likely to trust local governments, and hold other positive attitudes related to local and federal governments. Lastly, in a study of residents of Kansas City, Missouri, \citet{ho2017government} find that participants' perceived quality of the city website is strongly associated with their perceptions of the overall effectiveness of the City's communication with the public.

@@

\input{tables/stmTopWords2.tex} %\ref{tabSTMtopwords2}
